---
title: "Rapport SLA 1er février 2017"
author: "Yann de Rycke et Sarah F. Feldman"
output:
  word_document: default
  html_document: default
---
```{r setup, include=FALSE}
library(knitr)

opts_chunk$set(echo=FALSE, comment=NA, fig.width=6, fig.height=6)
#opts_chunk$set(fig.width=6, fig.height=6)
```

```{r allsource, echo=FALSE, message=FALSE}
.dir <- dirname(getwd())
source(paste0(.dir,"/src/libraries_SLA.R"))
source(paste0(.dir,"/src/fonctions_SLA.R"))
```


```{r, echo=FALSE}
#sla <- readRDS(paste0(.dir,"to push/sla_git/data/BASE_SLA_allbl.rds"))
sla <- readRDS(paste0(.dir,"/data/BASE_SLA_allbl.rds"))

sla$rilu <- ifelse (sla$DEBRILU < sla$DATEVNI & (is.na(sla$FINRILU) | sla$FINRILU>sla$DATEVNI), 1, 0) #je fais l'hyp qu'il n'y a pas de NA

sla$keep <- ifelse (sla$DATEVNI<=sla$ddn,1,0)

sla <- sla[sla$keep==1, ]
sla$time.vni <- as.numeric(sla$ddn - sla$DATEVNI)
sla$time.sym <- as.numeric(sla$ddn - sla$FIRSTSYMPTOM)
sla$evt <- ifelse (!is.na(sla$date_dc),1, 0)
# sex : 1 = 'Masculin' 2 = 'Feminin' => 0 = 'Masculin' 1 = 'Feminin'
sla$sex <- ifelse(sla$sex_def==1,0,sla$sex_def) #0 = 'Masculin' 1 = 'Feminin'
sla$sex <- ifelse(sla$sex_def==2,1,sla$sex) #0 = 'Masculin' 1 = 'Feminin'
sla$agevni <- round(as.numeric(sla$DATEVNI-sla$DOB)/365.25,0)
sla$rilu <- ifelse(sla$DATEVNI>sla$DEBRILU & !is.na(sla$DEBRILU), 1,0)
sla$rilu <- ifelse(sla$DATEVNI<sla$FINRILU & !is.na(sla$FINRILU), 0,sla$rilu)
sla$familial <- ifelse (is.na(sla$familial),0,sla$familial)
sla$LIEUDEB_recode <- as.factor(sla$LIEUDEB_recode)
#sla$ddn <- ifelse(sla$ddn>as_date("2015-08-27"), as_date("2015-08-27"), sla$ddn) #voir avec Yann

var_bl <- c("familial", "sex", "agevni", "LIEUDEB_recode", "rilu", "dysp","orthop","CVF_ASSIS_perc_pred","CVF_COUCHE_perc_pred","SNIP_cmH2O",
  "SNIP_perc_pred","PIMAX_cmH2O","PIMAX_perc_pred","perc_time_under_spo2_90","time_under_spo2_90_h","bicar","ALS_score","bulb_score")

var_quali <- c("familial", "sex", "LIEUDEB_recode", "rilu", "dysp", "orthop")
var_quanti <- var_bl [! var_bl %in% var_quali]

sla[,var_quanti] <- apply(sla[,var_quanti], 2, function(x) as.numeric(x))
sla[,var_quali[!var_quali%in% "LIEUDEB_recode"]] <- apply(sla[,var_quali[!var_quali%in% "LIEUDEB_recode"]], 2, function(x) as.numeric(x))
```

# Baselines all SLA patients 

```{r}
all_SLA <- readRDS(paste0(.dir,"/data/all_SLA_bl.rds"))
all_SLA$rilu <- ifelse (!is.na(all_SLA$DEBRILU), 1, 0) #je fais l'hyp qu'il n'y a pas de NA
all_SLA$rilu <- ifelse ((all_SLA$DEBRILU > all_SLA$DATEVNI & !is.na(all_SLA$DATEVNI) & !is.na(all_SLA$DEBRILU)), 0, all_SLA$rilu) #je fais l'hyp qu'il n'y a pas de NA
all_SLA$rilu <- ifelse (all_SLA$FINRILU < all_SLA$DATEVNI & !is.na(all_SLA$DATEVNI) & !is.na(all_SLA$FINRILU), 0, all_SLA$rilu)
all_SLA$keep <- ifelse ((all_SLA$DATEVNI<=all_SLA$ddn & !is.na(all_SLA$DATEVNI)) | is.na(all_SLA$DATEVNI),1,0)
all_SLA <- all_SLA[all_SLA$keep==1, ]
all_SLA$ddn <- as_date(all_SLA$ddn)
all_SLA$time.vni <- as.numeric(all_SLA$ddn - all_SLA$DATEVNI)
all_SLA$time.sym <- as.numeric(all_SLA$ddn - all_SLA$FIRSTSYMPTOM)
all_SLA$evt <- ifelse (!is.na(all_SLA$date_dc),1, 0)
# sex : 1 = 'Masculin' 2 = 'Feminin' => 0 = 'Masculin' 1 = 'Feminin'
all_SLA$sex <- ifelse(all_SLA$sex_def==1,0,all_SLA$sex_def) #0 = 'Masculin' 1 = 'Feminin'
all_SLA$sex <- ifelse(all_SLA$sex_def==2,1,all_SLA$sex) #0 = 'Masculin' 1 = 'Feminin'
all_SLA$agevni <- round(as.numeric(all_SLA$DATEVNI-all_SLA$DOB)/365.25,0)
all_SLA$rilu <- ifelse(all_SLA$DATEVNI>all_SLA$DEBRILU & !is.na(all_SLA$DEBRILU), 1,0)
all_SLA$rilu <- ifelse(all_SLA$DATEVNI<all_SLA$FINRILU & !is.na(all_SLA$FINRILU), 0,all_SLA$rilu)
all_SLA$familial <- ifelse (is.na(all_SLA$familial),0,all_SLA$familial)
all_SLA$LIEUDEB_recode <- as.factor(all_SLA$LIEUDEB_recode)

```

# Flowchart


# Range DATEVNI
```{r}
range(sla$DATEVNI,na.rm=T)
```

#range DATE FIRST SYMP

```{r}
range(sla$FIRSTSYMPTOM,na.rm=T)
```

# Patients characteristics

## Tous patients SLA
```{r}
table_var_quali <- lapply(var_quali, des_quali, all_SLA)
table_var_quali <- do.call(rbind,table_var_quali)

table_var_quanti <- lapply(var_quanti, des_quanti, all_SLA)
table_var_quanti <- do.call(rbind,table_var_quanti)

table_var <- rbind(table_var_quali,table_var_quanti)
kable(table_var)

```
pb : de nombreuses valeurs de base sont définies par rapport à la VNI...


## Patients SLA sous VNI
```{r, echo=FALSE}
table_var_quali <- lapply(var_quali, des_quali, sla)
table_var_quali <- do.call(rbind,table_var_quali)

table_var_quanti <- lapply(var_quanti, des_quanti, sla)
table_var_quanti <- do.call(rbind,table_var_quanti)

table_var <- rbind(table_var_quali,table_var_quanti)
kable(table_var)
```

Table 1 Patients characteristics at baseline (t(baseline) = NIV beginning)
*quantitative variables


# median follow-up from NIV beginning

median follow-up (year):

```{r, echo=FALSE, message=FALSE}
#suivi
s<-sla[!is.na(sla$time.vni),]
sym.suiv <- survfit(Surv(time.vni,1-evt)~1,data=s)
an <- paste0 (round(summary(sym.suiv)$table['median']/365.25,2)," [", round(summary(sym.suiv)$table['0.95LCL']/365.25,2),"-",round(summary(sym.suiv)$table['0.95UCL']/365.25,2),"]")
an
```

median follow-up (months):

```{r, echo=FALSE, message=FALSE}
#suivi
sym.suiv2 <- survfit(Surv((time.vni*12/365.25),1-evt)~1,data=s)
m <- paste0 (round(summary(sym.suiv2)$table['median'],2)," [", round(summary(sym.suiv2)$table['0.95LCL'],2),"-",round(summary(sym.suiv2)$table['0.95UCL'],2),"]")
m
```

# Survival from first symptoms

```{r}
s<-sla[!is.na(sla$time.sym),]
sym.surv <- survfit(Surv(time.sym,evt)~1, data=s, conf.int=.95)


# sym.surv2 <- survfit(Surv(time.sym*12/365.25,evt)~1, data=s, conf.int=.95)
# ggsurv(sym.surv2) +#https://www.r-bloggers.com/survival-plots-have-never-been-so-informative/
#   #scale_x_continuous(breaks=seq(0,max(s$time.sym),1), labels=0:(length(seq(0,max(s$time.sym),1))-1)) +
#   scale_y_continuous(labels=percent) +
#   labs(x="Time of follow-up, months") 

ggsurv(sym.surv) +#https://www.r-bloggers.com/survival-plots-have-never-been-so-informative/
  scale_x_continuous(breaks=seq(0,max(s$time.sym),365.25), labels=0:(length(seq(0,max(s$time.sym),365.25))-1)) +
  scale_y_continuous(labels=percent) +
  labs(x="Time of follow-up, years") 
```

Fig.2 Survival from first symptoms 

```{r}
#summary(sym.surv)
sv <- summary(sym.surv, time=(365*2))
df <- data.frame(time = sv$time/365 , survival = sv$surv*100, LCI = sv$lower*100, UCI = sv$upper*100)
df[,2:4] <- round(df[,2:4], 0)
cat(paste0(df$time, " years after first symptoms, survival[IC95%] ", df$survival, "% [",df$LCI,"% - ",df$UCI, "%]\n"))

```

median survival (year):

```{r, echo=FALSE, message=FALSE}
#suivi
s<-sla[!is.na(sla$time.sym),]
sym.surv <- survfit(Surv(time.sym,evt)~1, data=s, conf.int=.95)
an <- paste0 (round(summary(sym.surv)$table['median']/365.25,2)," [", round(summary(sym.surv)$table['0.95LCL']/365.25,2),"-",round(summary(sym.surv)$table['0.95UCL']/365.25,2),"]")
an
```

median follow-up (month):

```{r, echo=FALSE, message=FALSE}
#suivi
s<-sla[!is.na(sla$time.sym),]
sym.surv2 <- survfit(Surv(time.sym*12/365.25,evt)~1, data=s, conf.int=.95)
m <- paste0 (round(summary(sym.surv2)$table['median'],2)," [", round(summary(sym.surv2)$table['0.95LCL'],2),"-",round(summary(sym.surv2)$table['0.95UCL'],2),"]")
m
```

# Survival from NIV beginning

```{r}
s<-sla[!is.na(sla$time.vni),]
vni.surv <- survfit(Surv(time.vni,evt)~1, data=s, conf.int=.95)


# vni.surv2 <- survfit(Surv(time.vni*12/365.25,evt)~1, data=s, conf.int=.95)
# ggsurv(vni.surv2) +#https://www.r-bloggers.com/survival-plots-have-never-been-so-informative/
#   #scale_x_continuous(breaks=seq(0,max(s$time.vni),1), labels=0:(length(seq(0,max(s$time.vni),1))-1)) +
#   scale_y_continuous(labels=percent) +
#   labs(x="Time of follow-up, months") 

ggsurv(vni.surv) +#https://www.r-bloggers.com/survival-plots-have-never-been-so-informative/
  scale_x_continuous(breaks=seq(0,max(s$time.vni),365.25), labels=0:(length(seq(0,max(s$time.vni),365.25))-1)) +
  scale_y_continuous(labels=percent) +
  labs(x="Time of follow-up, years") 
```

Fig.3 Survival from NIV beginning 

```{r}
#summary(vni.surv)
sv <- summary(vni.surv, time=(365))
df <- data.frame(time = sv$time/365 , survival = sv$surv*100, LCI = sv$lower*100, UCI = sv$upper*100)
df[,2:4] <- round(df[,2:4], 0)
cat(paste0(df$time, " year(s) after beginning of NIV, survival[IC95%] ", df$survival, "% [",df$LCI,"% - ",df$UCI, "%]\n"))

```

median survival (year):

```{r, echo=FALSE, message=FALSE}
#suivi
s<-sla[!is.na(sla$time.vni),]
vni.surv <- survfit(Surv(time.vni,evt)~1, data=s, conf.int=.95)
an <- paste0 (round(summary(vni.surv)$table['median']/365.25,2)," [", round(summary(vni.surv)$table['0.95LCL']/365.25,2),"-",round(summary(vni.surv)$table['0.95UCL']/365.25,2),"]")
an
```

median survival (month):

```{r, echo=FALSE, message=FALSE}
#suivi
s<-sla[!is.na(sla$time.vni),]
vni.surv2 <- survfit(Surv(time.vni*12/365.25,evt)~1, data=s, conf.int=.95)
m <- paste0 (round(summary(vni.surv2)$table['median'],2)," [", round(summary(vni.surv2)$table['0.95LCL'],2),"-",round(summary(vni.surv2)$table['0.95UCL'],2),"]")
m
```

# Bivariate analysis : cox regressions

For all the following analysis, beginning = NIV

## Familial
```{r}
#check_RP (var="familial", data=sla, .time="time.vni", .evt="evt", type="quali")
draw_surv_bin(var="familial", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quali", surv_only = TRUE) 
Test_score_HR_IC(var="familial", data=sla, .time="time.vni", .evt="evt", type="quali", dep_temps = FALSE)
```

Proportionnal hazard hypothesis verified.


## Sex
```{r, eval=FALSE}
check_RP (var="sex", data=sla, .time="time.vni", .evt="evt", type="quali")
#tmp <- lapply(c("log","sqrt","*t","/t","2sqrt"),function(x){
tmp <- lapply("*t^0.7",function(x){
add_vart_and_check (var="sex", data=sla, .time="time.vni", .evt="evt", type="quali", recode=FALSE, .transf=x)  
})
cat(do.call(rbind,tmp))
```
Proportionnal hazard hypothesis not verified, time dependant variable added (var*t^0.7)

```{r}
draw_surv_bin(var="sex", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quali", surv_only = TRUE) 
```
0: male 1: female

```{r}
Test_score_HR_IC(var="sex", data=sla, .time="time.vni", .evt="evt", type="quali", recode=FALSE, dep_temps = TRUE, .transf="*t^0.7", vec_time=12)
```

## Riluzole
```{r, eval=FALSE}
check_RP (var="rilu", data=sla, .time="time.vni", .evt="evt", type="quali")
```

Proportionnal HR hypothesis verified
```{r}
draw_surv_bin(var="rilu", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quali", surv_only = TRUE) 
```


```{r}
Test_score_HR_IC(var="rilu", data=sla, .time="time.vni", .evt="evt", type="quali", dep_temps = FALSE)
```

## Rest dyspnoea

```{r, eval=FALSE}
check_RP (var="dysp", data=sla, .time="time.vni", .evt="evt", type="quali")
tmp <- lapply(c("log"),function(x){
add_vart_and_check (var="dysp", data=sla, .time="time.vni", .evt="evt", type="quali", recode=FALSE, .transf=x)  
})
cat(do.call(rbind,tmp))
```

Proportionnal hazard hypothesis not verified, time dependant variable added (var*var(t), transf=log). Log don't suit completely (curve not perfect).
```{r}
draw_surv_bin(var="dysp", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quali", surv_only = TRUE) 
```
```{r}
Test_score_HR_IC(var="dysp", data=sla, .time="time.vni", .evt="evt", type="quali", recode=FALSE, dep_temps = TRUE, .transf="log", vec_time=24)
```

Score test significant but HR include 1...

## Orthopnea

```{r, eval=FALSE}
check_RP (var="orthop", data=sla, .time="time.vni", .evt="evt", type="quali")
Test_score_HR_IC(var="orthop", data=sla, .time="time.vni", .evt="evt", type="quali", recode=FALSE, dep_temps = FALSE)
```
```{r}
draw_surv_bin(var="orthop", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quali", surv_only = TRUE)
```

Proportionnal hazard hypothesis verified.

## onset localisation
#### Recodage en 4 variables binaires

```{r, echo=FALSE}
s <- sla
s$tps <- (s$time.vni/365.25) + 0.001 # au cas ou un temps vaut 0 ce qui empêche survsplit de fonctionner
s <- s[!is.na(s$LIEUDEB_recode),]
#recodage LIEUDEB en 4 var bianaire. ref = bulbar
s$cerv <- ifelse(s$LIEUDEB_recode=="cervical",1,0)
s$llimb <- ifelse(s$LIEUDEB_recode=="lower limb onset", 1, 0)
s$resp <- ifelse(s$LIEUDEB_recode=="respiratory", 1, 0)
s$ulimb <- ifelse(s$LIEUDEB_recode=="upper limb onset", 1, 0)

cox <- coxph(Surv(tps, evt) ~ cerv + llimb + resp + ulimb, data = s)
```
```{r, eval=FALSE}
#résidus de Shoenfeld non significatif?
zt <- cox.zph(cox, transf="identity")
for (i in 1:(nrow(zt$table)-1)){
  iz<-i
  plot(zt[iz])
  abline(h=0, col="red")
}

#Test de Harrell non significatif?
zit <- cox.zph(cox, transform = "rank")
zit

tmp <- lapply(c("log","sqrt","*t","/t","*t^2"),function(x){
add_vart_and_check (var="llimb", data=s, .time="time.vni", .evt="evt", type="quali", recode=FALSE, .transf=x)
})
cat(do.call(rbind,tmp))

ti <- sort(unique(c(0,s$tps[s$evt==1])))
slat <- s
slat$start <- 0
slat$stop <- slat$tps
slat$evt <- slat$evt
#slat <- survSplit(slat, end="stop", event="evt", start="start",cut=ti) #Yann
slat <- survSplit(Surv(stop,evt)~.,slat,start="start",cut=ti)           #Sarah

#s$cerv : log
#s$resp : rien
#s$ulimb : rien
#s$llimb :t^2

```

PHH not verified, couldn't correct variable

```{r}
surv_lieudeb (surv_only=TRUE)
Test_score_HR_IC(var="LIEUDEB_recode", data=sla, .time="time.vni", .evt="evt", type="quali2", recode=FALSE, dep_temps = FALSE)
```

## agevni

```{r}
# check_loglin (var="agevni", data=sla, .time="time.vni", .evt="evt")
# check_RP(var="agevni", data=sla, .time="time.vni", .evt="evt", type="quanti", recode = FALSE)
# tmp <- lapply(c("log","sqrt","*t","/t","*t^0.7"),function(x){
# add_vart_and_check (var="agevni", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, .transf=x)
# })
# cat(do.call(rbind, tmp))
Test_score_HR_IC(var="agevni", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, dep_temps = FALSE)

```
Loglinearity hypothesis verified.
Proportionnality not verified, variable cannot be corrected. 

## CVF_ASSIS_perc_pred

```{r}
#check_loglin (var="CVF_ASSIS_perc_pred", data=sla, .time="time.vni", .evt="evt")
# check_RP(var="CVF_ASSIS_perc_pred", data=sla, .time="time.vni", .evt="evt", type="quanti", recode = FALSE)
# tmp <- lapply(c("log","sqrt","*t","/t","*t^3"),function(x){
# add_vart_and_check (var="CVF_ASSIS_perc_pred", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, .transf=x)
# })
# cat(do.call(rbind, tmp))
Test_score_HR_IC(var="CVF_ASSIS_perc_pred", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, dep_temps = TRUE, vec_time=12, .transf="*t^3")
```
Loglinearity hypothesis verified.
Proportionnality not verified, variable corrected with t^3 (not perfect)

## CVF_COUCHE_perc_pred
```{r}
#check_loglin (var="CVF_COUCHE_perc_pred", data=sla, .time="time.vni", .evt="evt")
# check_RP(var="CVF_COUCHE_perc_pred", data=sla, .time="time.vni", .evt="evt", type="quanti", recode = FALSE)
# tmp <- lapply(c("log","sqrt","*t","/t","*t^2"),function(x){
# # tmp <- lapply(c("*t^0.7"),function(x){
#  add_vart_and_check (var="CVF_COUCHE_perc_pred", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, .transf=x)
#  })
# cat(do.call(rbind, tmp))
Test_score_HR_IC(var="CVF_COUCHE_perc_pred", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, dep_temps = FALSE)
```
Loglinearity hypothesis verified.
Proportionnality not verified, variable cannot be corrected (results without correction)

## SNIP_cmH2O
```{r}
# check_loglin (var="SNIP_cmH2O", data=sla, .time="time.vni", .evt="evt")
# check_RP(var="SNIP_cmH2O", data=sla, .time="time.vni", .evt="evt", type="quanti", recode = FALSE)
# tmp <- lapply(c("log","sqrt","*t","/t","*t^2"),function(x){
# # tmp <- lapply(c("*t^0.7"),function(x){
#  add_vart_and_check (var="SNIP_cmH2O", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, .transf=x)
#  })
# cat(do.call(rbind, tmp))
Test_score_HR_IC(var="SNIP_cmH2O", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, dep_temps = TRUE, vec_time=12, .transf="*t")
```
Loglinearity hypothesis verified.
Proportionnality not verified, variable corrected with t (not perfect)

## SNIP_perc_pred
```{r}
#check_loglin (var="SNIP_perc_pred", data=sla, .time="time.vni", .evt="evt")
# check_RP(var="SNIP_perc_pred", data=sla, .time="time.vni", .evt="evt", type="quanti", recode = FALSE)
# tmp <- lapply(c("log","sqrt","*t","/t","*t^2"),function(x){
# # tmp <- lapply(c("*t^0.7"),function(x){
#  add_vart_and_check (var="SNIP_perc_pred", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, .transf=x)
#  })
# cat(do.call(rbind, tmp))
Test_score_HR_IC(var="SNIP_perc_pred", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=FALSE, dep_temps = TRUE, vec_time=12, .transf="*t^2")
```
Loglinearity hypothesis verified.
Proportionnality not verified, variable corrected with t^2 (not perfect)

## PIMAX_cmH2O
```{r}
.var <- "PIMAX_cmH2O"
.recode <- TRUE
.dep_temps <- TRUE
.transf <- "*t"
# check_loglin (var="PIMAX_cmH2O", data=sla, .time="time.vni", .evt="evt")
# check_RP(var="PIMAX_cmH2O", data=sla, .time="time.vni", .evt="evt", type="quanti", recode = .recode)
# tmp <- lapply(c("log","sqrt","*t","/t","*t^2"),function(x){
# # tmp <- lapply(c("*t^0.7"),function(x){
#  add_vart_and_check (var="PIMAX_cmH2O", data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, .transf=x)
#  })
# cat(do.call(rbind, tmp))

Test_score_HR_IC(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, dep_temps = .dep_temps, vec_time=12, .transf=.transf)
```
Loglinearity not verified. Variable transformed in binary variable (median).
Proportionnality not verified, variable corrected with *t (not perfect)

```{r}
draw_surv_bin(var=.var, data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quanti", surv_only = TRUE) 
```


## PIMAX_perc_pred
```{r}
.var <- var_quanti[7]
.recode <- FALSE
.dep_temps <- TRUE
.transf <- "*t^3"

# check_loglin (var=.var, data=sla, .time="time.vni", .evt="evt")
# check_RP(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode = .recode)
# tmp <- lapply(c("log","sqrt","*t","/t","*t^3"),function(x){
#   # tmp <- lapply(c("*t^0.7"),function(x){
#   add_vart_and_check (var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, .transf=x)
# })
# cat(do.call(rbind, tmp))

Test_score_HR_IC(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, dep_temps = .dep_temps, vec_time=12, .transf=.transf)

```

## perc_time_under_spo2_90
```{r}
.var <- var_quanti[8]
.recode <- FALSE
.dep_temps <- FALSE
.transf <- NULL

# check_loglin (var=.var, data=sla, .time="time.vni", .evt="evt")
# check_RP(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode = .recode)
# tmp <- lapply(c("log","sqrt","*t","/t","*t^3"),function(x){
#   # tmp <- lapply(c("*t^0.7"),function(x){
#   add_vart_and_check (var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, .transf=x)
# })
# cat(do.call(rbind, tmp))

Test_score_HR_IC(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, dep_temps = .dep_temps, vec_time=12, .transf=.transf)

```


## time_under_spo2_90_h

```{r}
.var <- var_quanti[9]
.recode <- FALSE
.dep_temps <- FALSE
.transf <- NULL

#  check_loglin (var=.var, data=sla, .time="time.vni", .evt="evt")
# check_RP(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode = .recode)
# if (.dep_temps==TRUE) {tmp <- lapply(c("log","sqrt","*t","/t","*t^3"),function(x){
#   # tmp <- lapply(c("*t^0.7"),function(x){
#   add_vart_and_check (var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, .transf=x)
# })
# cat(do.call(rbind, tmp))}

Test_score_HR_IC(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, dep_temps = .dep_temps, vec_time=12, .transf=.transf)

```


## bicar
```{r}
.var <- var_quanti[10]
.recode <- FALSE
.dep_temps <- FALSE
.transf <- NULL

#  check_loglin (var=.var, data=sla, .time="time.vni", .evt="evt")
# check_RP(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode = .recode)
# if (.dep_temps==TRUE) {tmp <- lapply(c("log","sqrt","*t","/t","*t^3"),function(x){
#   # tmp <- lapply(c("*t^0.7"),function(x){
#   add_vart_and_check (var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, .transf=x)
# })
# cat(do.call(rbind, tmp))}

Test_score_HR_IC(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, dep_temps = .dep_temps, vec_time=12, .transf=.transf)
```

## ALS_score
```{r}
.var <- var_quanti[11]
.recode <- FALSE
.dep_temps <- TRUE
.transf <- "*t^3"

# check_loglin (var=.var, data=sla, .time="time.vni", .evt="evt")
# check_RP(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode = .recode)
# if (.dep_temps==TRUE) {tmp <- lapply(c("log","sqrt","*t","/t","*t^3"),function(x){
#   # tmp <- lapply(c("*t^0.7"),function(x){
#   add_vart_and_check (var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, .transf=x)
# })
# cat(do.call(rbind, tmp))}

Test_score_HR_IC(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, dep_temps = .dep_temps, vec_time=12, .transf=.transf)
```
t^3 fit approximatively (but not perfect)

## bulb_score
```{r}
.var <- var_quanti[12]
.recode <- TRUE
.dep_temps <- FALSE
.transf <- NULL

# check_loglin (var=.var, data=sla, .time="time.vni", .evt="evt")
# check_RP(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode = .recode)
# if (.dep_temps==TRUE) {tmp <- lapply(c("log","sqrt","*t","/t",.transf),function(x){
#   # tmp <- lapply(c("*t^0.7"),function(x){
#   add_vart_and_check (var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, .transf=x)
# })
# cat(do.call(rbind, tmp))}

Test_score_HR_IC(var=.var, data=sla, .time="time.vni", .evt="evt", type="quanti", recode=.recode, dep_temps = .dep_temps, vec_time=12, .transf=.transf)
```
Proportionnality not verified but no correction fit, in consequent, I analyzed it without adding time correction. 

```{r}
draw_surv_bin(var=.var, data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quanti", surv_only = TRUE, pvalue = TRUE, dep_temps = TRUE, .transf="*t") 
```


# Plots 

```{r}
draw_surv_bin(var="familial", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quali", pvalue = TRUE) 
```
```{r}
draw_surv_bin(var="sex", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type="quali", pvalue=TRUE, dep_temps = TRUE, .transf="*t^0.7")
```
```{r}
draw_surv_bin(var="rilu", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quali", pvalue = TRUE) 
```
```{r}
draw_surv_bin(var="dysp", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type="quali", pvalue=TRUE, dep_temps = TRUE, .transf="log")

```
```{r}
draw_surv_bin(var="orthop", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quali", pvalue = TRUE)

```
```{r, fig.width=8, fig.height=8}
surv_lieudeb (surv_only=FALSE, pvalue=TRUE)
```

```{r, fig.width=8, fig.height=8}
draw_surv_bin(var="PIMAX_cmH2O", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quanti", surv_only = FALSE, pvalue = TRUE, dep_temps = TRUE, .transf="*t") 
```
```{r, fig.width=8, fig.height=8}
draw_surv_bin(var="bulb_score", data=sla, .time="time.vni", .evt="evt", vec_time_IC= 1, type = "quanti", surv_only = FALSE, pvalue = TRUE)
```